Number recognition for use in a Sudoku solver

### 2012-03-15 doc/icml2010stylefiles/paper.tex
worked on svm part in doc

@@

\section{Introduction}
Number and letter recognition is key in many real-world applications. Digitalizing print media, automated sorting of letters, or recognition of signs in robotics or driver assistance systems require well performing algorithms for character recognition. In the following we analyze the performance of different techniques for number recognition, namely Neural Networks, Support Vector Machines and Logistic Regression, by using them in an automated Sudoku solver.

@@

\section{Generation of Training Data}
\subsection{Image Generation}
\begin{figure}[ht]
	\centerline{\includegraphics[scale=0.25]{examples}}
	\caption{Examples of generated numbers}
	\label{fig:generated_numbers}
\end{figure}
\subsection{Image Processing}

\section{Training}
\subsection{Neural Network}
\begin{figure}[ht]
	\centerline{\includegraphics[width=\columnwidth, trim=0 30 0 30]{nn}}
	\caption{Neural Network with one hidden layer}
	\label{fig:nn}
\end{figure}
\subsection{Support Vector Machine}
\subsection{Logistic Regrssion}

@@

>>>>

% custom imports
\usepackage{amsmath}

@@

\section{Introduction}
Number and letter recognition is key in many real-world applications. Digitalizing print media, automated sorting of letters, or recognition of signs in robotics or driver assistance systems require well performing algorithms for character recognition. In the following we analyze the performance of different techniques for number recognition, namely Neural Networks, Support Vector Machines and Logistic Regression, by using them in an automated sudoku solver.

@@

\section{Generation of Training Data}
\subsection{Image Generation}
\begin{figure}[ht]
	\centerline{\includegraphics[scale=0.25]{examples}}
	\caption{Examples of generated numbers}
	\label{fig:generated_numbers}
\end{figure}

\subsection{Image Processing}

\section{Training}
\subsection{Neural Network}
\begin{figure}[ht]
	\centerline{\includegraphics[width=\columnwidth, trim=0 30 0 30]{nn}}
	\caption{Neural Network with one hidden layer}
	\label{fig:nn}
\end{figure}
\subsection{Support Vector Machines}
The next technique we applied to the discussed problem are Support Vector Machines \cite{Bishop200608} which try to solve the following optimization problem:
\begin{align*}
\min_{w,b} &~~ \frac{1}{2}||w||^2 + C \sum_{i=1}^{n} \xi_i\\
\text{subject to } &~~ y_i(w^T \phi(x_i) + b) - 1 + \xi_i \ge 0\\
\text{and} &~~ \xi_i \ge 0.
\end{align*}
Using a radial basis function (RBF) as kernel we performed a grid search over $C$ and $\gamma$ to find those parameters that provide the highest accuracy on the validation set. We used the open source library ``libsvm'' \cite{chang2011libsvm} wrapped by some octave scripts for setting up data sets and performing the grid search.
\subsection{Logistic Regression}

@@

\section{References}
